Model exploration

### 2015-03-12 documentation/model_exploration.Rmd
update model exploration

par(mfrow = c(2,2), bty ="n", las = 1 ) 
defplot(rho, G(rho), ylab = "plant mortality/growth", col = colpal$grow[1])
lines(rho, C(rho, set = list(L = 2)), col = colpal$mort[1] )
lines(rho, C(rho, set = list(L = 5)), col = colpal$mort[1] )
lines(rho, C(rho, set = list(L = 8)), col = colpal$mort[1] )

@@

par(mfrow = c(1,2), bty ="n", las = 1 ) 
parms <- defparms
parms$f = 0.9
parms$b = 0.4

attractor(parms)

@@

attractor(parms)

@@

parms$L = 8
parms$p = 0.8

attractor(parms)

@@

parms$L = 6
parms$q = 0
parms$v = 0.9

attractor(parms)

>>>>

par(mfrow = c(2,2), bty ="n", las = 1 )

defplot(rho, G(rho), ylab = "plant mortality/growth", col = colpal$grow[1])
lines(rho, C(rho, set = list(L = 2)), col = colpal$mort[1] )
lines(rho, C(rho, set = list(L = 5)), col = colpal$mort[1] )
lines(rho, C(rho, set = list(L = 8)), col = colpal$mort[1] )

@@

par(mfrow = c(1,2), bty ="n", las = 1 ) 
parms <- defparms
parms$f = 0.8
parms$b = 0.3

attractor(parms, pairapprox = FALSE, localvals = TRUE)

bifurcation(parms, pairapprox = TRUE, "b", c(0,1))

@@

attractor(parms,  pairapprox = FALSE, localvals = TRUE)

bifurcation(parms, pairapprox = TRUE, "b", c(0,1))

@@

parms$L = 8
parms$p = 0.7

attractor(parms, pairapprox = FALSE, localvals = TRUE)

bifurcation(parms, pairapprox = TRUE, "L", c(0,12))

@@

parms$L = 6
parms$q = 0.5
parms$v = 0.9

attractor(parms, pairapprox = FALSE, localvals = TRUE)

bifurcation(parms, pairapprox = FALSE, "L", c(0,12))
